A survey of HTTP caching options on the open Web

### 2014-12-17 sanity/paper1.tex
describe hitlist headers operation
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@903 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

@@

Then, we retrieved the dataset of the Billion Triple Challenge
2014\todo{ref}, a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps. Due to the presence of invalid RDF, we
iterated through the NQuad files on a line-by-line basis. First, we
matched each line against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework \text{RDF::Trine}\todo{footnote} was used to parse
the line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \texttt{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \texttt{void:vocabulary},
\texttt{rdfa:vocabulary} or \texttt{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \texttt{cogs:Endpoint},
\texttt{owl:Ontology} and \texttt{voaf:Vocabulary} \todo{footnotes for
  all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

@@

>>>>

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\httph}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

@@

LDF\todo{ref} asserted that SPARQL query caching is only possible on a
per-query basis, but future research should challenge this
assumption. With this in mind, if reasoning is not involved, we note
that ontologies are not relevant to query answering since they usually
occur in bound terms. It is interesting to understand caching when
this is not the case. Moreover, many ontologies are maintained by a
small group of humans and change seldomly.

@@

Then, we retrieved the dataset of the Billion Triple Challenge
2014\todo{ref}, a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. Due to the presence of invalid RDF, we
iterated through the NQuad files on a line-by-line basis. First, we
matched each line against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework \text{RDF::Trine}\todo{footnote} was used to parse
the line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \rdfterm{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \rdfterm{void:vocabulary},
\rdfterm{rdfa:vocabulary} or \rdfterm{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \rdfterm{cogs:Endpoint},
\rdfterm{owl:Ontology} and \rdfterm{voaf:Vocabulary} \todo{footnotes for
  all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

@@

We then sought to classify resources into the categories ``endpoint''
for SPARQL endpoints, ``vocabulary'' for ontologies, ``dataset'' for
datasets that may contain further descriptions of several resources,
or simply ``inforesources'' for those that did not fit in the above
classes. To do so, we classified based on certain predicates and
classes, see table\todo{create table}. Additionally, URIs derived from
prefix.cc were classified as ``vocabulary'' and those from SPARQLES as
``endpoint''.

Since we blatantly violated URI opacity with our regular expression
matching in the first step, we needed to further filter candidates for
SPARQL endpoints. This step therefore included filtering as well as
classification.

We found in the data a large number of ontologies that consist of many
information resources with just a few triples in each. Since they
appear to be produced by the same software, usually Semantic
Mediawiki, we assume that they are configured with a single setup, and
thus we will merely sample these resources.

We continued to also sample the HTTP headers gathered in the BTC2014
dataset. 
%as they had recorded some of the relevant headers,
%\httph{Expires}, \httph{Last-Modified} and \httph{ETag}. 
First, we traversed the files with a simple UNIX \texttt{grep} to find
the resources that had reported one of the RDF serializations as
content type. We then traversed this list, first discarded the
resources that did not have a valid IRI (this amounted to just 3273
resources). For the resources we found, as well as for the resources
that was of \rdfterm{rdf:type owl:Ontology} above, we kept one
resource per hostname, with the exception of the popular blogging
platforms Livejournal and SAPO, where each blog has their own host and
they expose FOAF data. For those, we only kept one hostname.
